### 2020-11-04 README.Rmd
start functions to raster reading
submission

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Assessing the spatial patterning of Middle Paleolithic human settlement in westernmost Iberia

@@

> Cascalheira, J., Bicho, N. and Gonçalves. C., (2018). _Assessing the spatial patterning of Middle Paleolithic human settlement in westernmost Iberia_. Name of journal/book <https://doi.org/xxx/xxx>

Our pre-print is online here:

> Cascalheira, J., Bicho, N. and Gonçalves. C., (2018). _Assessing the spatial patterning of Middle Paleolithic human settlement in westernmost Iberia_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

> Cascalheira, J., Bicho, N. and Gonçalves. C., (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for _Assessing the spatial patterning of Middle Paleolithic human settlement in westernmost Iberia_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

### How to download or install

You can download the compendium as a zip from from this URL: <https://github.com/jmcascalheira/MidPalSet/archive/master.zip>

Or you can install this compendium as an R package, MidPalSet, from GitHub with:
```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("jmcascalheira/MidPalSet")
```
### Licenses

>>>>

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "The spatial patterning of Middle Paleolithic human settlement in Western Iberia"

```

# The spatial patterning of Middle Paleolithic human settlement in Western Iberia

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh///master?urlpath=rstudio)

@@

> Cascalheira, J., Gonçalves, C. and Maio D. (2020). _`r Title`_. Quaternary International <https://doi.org/10.1016/j.quaint.2020.08.027>

@@

> Cascalheira, J., Gonçalves, C. and Maio D., (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.17605/OSF.IO/456EG>

## Contents

The **analysis** directory contains:

  - [:file\_folder: paper](/analysis/paper): R Markdown source document
    for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis. It also has a rendered version,
    `paper.docx`, suitable for reading (the code is replaced by figures
    and tables in this file)
  - [:file\_folder: data](/analysis/data): Data used in the analysis.
  - [:file\_folder: figures](/analysis/figures): Plots and other
    illustrations
  - [:file\_folder:
    supplementary-materials](/analysis/supplementary-materials):
    Supplementary materials including notes and other documents
    prepared and collected during the analysis.

## How to run in your broswer or download and run locally

This research compendium has been developed using the statistical programming
language R. To work with the compendium, you will need
installed on your computer the [R software](https://cloud.r-project.org/)
itself and optionally [RStudio Desktop](https://rstudio.com/products/rstudio/download/).

The simplest way to explore the text, code and data is to click on
[binder](https://mybinder.org/v2/gh///master?urlpath=rstudio)
to open an instance of RStudio in your browser, which will have the
compendium files ready to work with. Binder uses rocker-project.org
Docker images to ensure a consistent and reproducible computational
environment. These Docker images can also be used locally.

You can download the compendium as a zip from from this URL:
[master.zip](/archive/master.zip). After unzipping:
- open the `.Rproj` file in RStudio
- run `devtools::install()` to ensure you have the packages this analysis depends on (also listed in the
[DESCRIPTION](/DESCRIPTION) file).
- finally, open `analysis/paper/paper.Rmd` and knit to produce the `paper.docx`, or run `rmarkdown::render("analysis/paper/paper.Rmd")` in the R console

### Licenses
